---
title: "Chapter1"
author: "Safouane Chergui"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(asaur)
library(dplyr)

gastricXelox

# 32 had the event
n_event <- gastricXelox %>% 
  select(delta) %>% 
  sum(.)

# The number of person-weeks: 999
person_weeks <- gastricXelox %>% 
  tally(timeWeeks)
  
# The event rate per person-week
# https://sph.unc.edu/files/2015/07/nciph_ERIC4.pdf
rate <- n_event / person_weeks
```

The packages loaded below are needed to execute the code in this file.

```{r}
library(asaur)
library(dplyr)
```

## 1st exercise

The dataset listing the patient, the survival time as well as the censoring indicator.

```{r cars}
patient_data <- data.frame(
  "Patient" = 1:5,
  "SurvTime" = c(5, 5, 4, 3, 1),
  "Status" = c(0, 0, 1, 1, 1)
)

patient_data
```


```{r}
dead <- sum(patient_data$Status)
```
The number of deceased persons during the trial is `r dead`.

Person-years in the trial: is a summary statistic that can be calculated by summing the total survival time of all patients in the trial (https://www.eupati.eu/glossary/patient-years/)

```{r}
person_years <- sum(patient_data$SurvTime)
```
Person-years is equal to `r person_years`.

The death rate per person-year: As the name of the statistic suggests, one has to divide the number of dead persons during the trial by the previously calculated statistic person_years.

```{r}
death_rate <- dead / person_years
```
The death rate is `r death_rate`.

## 2nd exercise


```{r}
n_event <- gastricXelox %>% 
  select(delta) %>% 
  sum(.)
```

The number of persons that had the event is `r n_event`.

The gastricXelox dataset contains only phase 2 clinical trial.

```{r}
person_weeks <- sum(gastricXelox$timeWeeks)
```
The number of person-weeks is `r person_weeks`.

The event rate per person-week is a similar idea to death-rate that we've calculated in the 1st exercise.
```{r}
event_rate <- n_event / person_weeks
```
The event rate per person-week is `r event_rate`.